### 2023-05-09 bachelorthesis/50-closure.tex
#39: Closre with work of thesis

% 6. Closure

@@

>>>>

% 5. Closure

@@

In this thesis the minimal resolution for simulations with GKW in the Cyclone Base parameter were observed in which the number of grid points for the parallel velocity $\Nvpar$ could be reduced from 64 to 48. \bigskip

Additional the active development of an restart script in \texttt{python} leads to further convenience during the performance of a simulation on the \texttt{btrzx1} cluster. \bigskip
